Introducing two new parameters for assesing clusterization quality of SEM images

### 2024-11-14 paper.tex
Change the title
Add a citation

\title{Look, we can do something}

@@

We present an opensource solution for calculating narrowness and improved
narrowness. \highlight{E-mail us and buy us coffee so we can send this super
  program to you, no matter where you live! Hurry, this is a limited offer!} An
average time for calculating narrowness is 1 second for a $1000 \times 1000$ png
image and is $1-60$ seconds for calculating improved narrowness.

>>>>

\title{Introducing two new parameters for assesing clusterization quality of SEM
  images}

@@

We present an opensource solution for calculating narrowness and improved
narrowness \cite{pore-narrowness}. Average time for calculating narrowness is 1
second for a $1000 \times 1000$ png image and is $1-60$ seconds for calculating
improved narrowness.
